The Minimal Retroreflective Microfacet Model

### 2025-09-26 article.tex
note that albedos are identical and that BTDF/BRDF combinations are possible for forwared and retro reflective variants

@@

>>>>

We further note that under our requirement of a reflection-symmetric microfacet normal distribution, the geometric
configurations for $\vecv$ and $\vecvv$ are identical.
Hence we can conclude $\rho_r(\vecv) = \rho_r(\vecvv)$ and $\rho_t(\vecv) = \rho_t(\vecvv)$, which in turn implies that the albedos of forward and retro-reflection are the same, i.e. $\rho_{r, \text{retro}}(\vecv) = \rho_r(\vecv)$ and $\rho_{t, \text{retro}}(\vecv) = \rho_t(\vecv)$.

@@

\paragraph*{Combination of BRDF and BTDF}

The albedo is identical for forward- and retro-reflective BRDF as well as BTDF,
which allows to arbitrarily combine forward- and retro-reflective variants into a BSDF.
When constructing an artist-controllable retro-reflective dielectric BSDF, we observed that using $f_t$ instead of $f_{t, \text{retro}}$ yields more intuitive results, in particular for an index of refraction close to 1.
